*Supplementary Material 1*

### 2022-02-25 ms/si.Rmd
Read fossils from ftol cache

tar_load(
  c(
    sanger_alignment_tbl,
    sanger_sampling,
    sanger_accessions_selection,
    plastome_tree,
    plastid_tree_dated,
    fossil_calibration_tips,
    ppgi_taxonomy,
    monophy_by_clade,
    acc_table_long,
    plastome_seqs_combined_filtered,
    sanger_tree_rooted,
    fossil_calibrations_for_treepl,
    sanger_tree_dated),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    gb_species_by_year,
    ref_files,
    other_dates,
    du_dates_all,
    family_stem_ages,
    fossil_ferns_raw,
    pteridocat_ppgi_diff_refs_out,
    pteridocat_ppgi_diff_notes,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    spermato_trees
  ),
  store = here::here("_targets")
)
```

@@

```{r fossils-make}
# Filter raw fossil data to just fossils used, write out as CSV
fossils_table <-
  fossil_ferns_raw %>%
  inner_join(
    select(fossil_calibration_tips, fossil_taxon), by = "fossil_taxon") %>%
  verify(nrow(.) == nrow(fossil_calibration_tips)) %>%
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference
  )
```

>>>>

tar_load(
  c(
    sanger_alignment_tbl,
    sanger_sampling,
    sanger_accessions_selection,
    plastome_tree,
    plastid_tree_dated,
    fossil_calibration_tips,
    ppgi_taxonomy,
    monophy_by_clade,
    acc_table_long,
    plastome_seqs_combined_filtered,
    sanger_tree_rooted,
    fossil_calibrations_for_treepl,
    sanger_tree_dated,
    fossil_ferns_all),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    gb_species_by_year,
    ref_files,
    other_dates,
    du_dates_all,
    family_stem_ages,
    pteridocat_ppgi_diff_refs_out,
    pteridocat_ppgi_diff_notes,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    spermato_trees
  ),
  store = here::here("_targets")
)
```

@@

```{r fossils-make}
# Filter raw fossil data to just fossils used, write out as CSV
fossils_table <-
  fossil_ferns_all %>%
  inner_join(
    unique(select(fossil_calibration_tips, n_fos)), by = "n_fos") %>%
  verify(nrow(.) == nrow(fossil_calibration_tips)) %>%
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference
  )
```
